\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2015-12-17 write_up/cricket.tex
added english season data

This isn't a comprehensive inventory of analyses that one could do on the topic. But neither is it meant to be. There are some simple questions that still unanswered. For one, how does the toss advantage vary over time? Have teams become smarter? Other more nuanced but commonly thought questions also remain. For one, students of the game suspect that the advantage of winning a toss in early English season is especially great. We propose to investigate these questions in a follow-up piece.

>>>>

This covers some of the more straightforward questions. Other more nuanced but commonly thought questions remain. For one, students of the game suspect that the advantage of winning a toss in early English season is especially great. We next check that using data on International matches from England.

\begin{figure}[htbp]
\centering
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Month in England}
\includegraphics[scale=.85]{../figs/winbyMonthEngland.pdf}
\label{fig:season}
\end{figure}

This isn't a comprehensive inventory of analyses that one could do on the topic. But neither is it meant to be. Some simple questions still remain unanswered. For one, how does the toss advantage vary over time? Have teams become smarter?  We propose to investigate these questions in a follow-up piece.
